\Large\textbf{Advection versus diffusion in brain ventricular transport}

### 2025-04-15 paper/main.tex
add ref

Ciliary motion is integral to physiological CSF flow,
and motile-cilia deficiency has been
associated with defective brain development and various
pathologies in zebrafish, rodents and humans~\cite{Eichele2020Cilia-drivenVentricle,
Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles,
Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
Sawamoto2006NewBrain, Yoshiba2014RolesSymmetry,
Hirokawa2006NodalAsymmetry, Youn2018PrimaryDiseases,
Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}.  As observed both experimentally and
computationally, absence of motile cilia alters CSF flow patterns
\Crefpanels{fig:fig1}{g}~\cite{Olstad2019CiliaryDevelopment}. We
next investigate the implications of these changes on brain ventricular
transport. We experimentally measured the movement of proteins by
monitoring photoconverted Dendra2 signal in control zebrafish and
motile-cilia mutant \emph{schmalhans} (\emph{smh}) zebrafish.  In ROIs
2 and 4, which quantify Dendra2 distribution downstream of the
photoconversion site, we observed a slower increase of fluorescence
intensity (\Crefpanels{fig:fig4}{a}): the mean times-to-threshold in
the \emph{smh} mutants were $45\%$ (ROI 2) and $25\%$ (ROI 4) higher
compared to controls (\Crefpanels{fig:fig4}{b}). We found no
significant differences between \emph{smh} mutants and controls in the
Dendra2 distribution in ROIs 3, 5, and 6.

>>>>

Ciliary motion is integral to physiological CSF flow,
and motile-cilia deficiency has been
associated with defective brain development and various
pathologies in zebrafish, rodents and humans~\cite{Eichele2020Cilia-drivenVentricle,
Olstad2019CiliaryDevelopment, Faubel2016Cilia-basedVentricles,
Guirao2010CouplingCilia, Afzelius2004CiliaRelatedDiseases,
Sawamoto2006NewBrain, Yoshiba2014RolesSymmetry,
Hirokawa2006NodalAsymmetry, Youn2018PrimaryDiseases,
Ma2024CiliaDisease, Ibanez-Tallon2002LossHydrocephalus}.  As observed both experimentally and
computationally, absence of motile cilia alters CSF flow patterns
\Crefpanels{fig:fig1}{g}~\cite{Olstad2019CiliaryDevelopment}. We
next investigate the implications of these changes on brain ventricular
transport. We experimentally measured the movement of proteins by
monitoring photoconverted Dendra2 signal in control zebrafish and
motile-cilia mutant \emph{schmalhans} (\emph{smh}, \emph{ccdc103}) zebrafish\cite{Panizzi2012Mutations}.
In ROIs 2 and 4, which quantify Dendra2 distribution downstream of the
photoconversion site, we observed a slower increase of fluorescence
intensity (\Crefpanels{fig:fig4}{a}): the mean times-to-threshold in
the \emph{smh} mutants were $45\%$ (ROI 2) and $25\%$ (ROI 4) higher
compared to controls (\Crefpanels{fig:fig4}{b}). We found no
significant differences between \emph{smh} mutants and controls in the
Dendra2 distribution in ROIs 3, 5, and 6.
